Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-29 paper/paper.tex
quick pass on Section 4.2

\Mar{------------------------------------------- Eu estou aqui}

The rule reported in the first step satisfies the criterion to only
capture positive traffic. Unfortunately, that rule is overconstrained.
The rule can include options that are irrelevant for the input
message. Consequently, the \nids\ may be unable to capture a different
manifestation of the same attack.

@@

\tname{} leverages public data sets~\cite{tcpreplay} of benign traffic
to guide the search for more general rules, hence addressing the
overffiting issue. To that end, \tname{} \emph{minimizes} the rules
produced in the previous step, preserving the invariant of \emph{only}
capturing the positive malicious traffic. We say that a rule is
minimal if discarding any option results in capturing negative (\ie{},
benign) traffic.  The minimization procedure we propose in this step
builds on the observation that all options from the rule produced in
the previous step are satisifed by the positive traffic. Consequently,
any subset of these options also captures the positive traffic. The
procedure iteratively discards options from the candidate rule until
it detects that the rule is minimal, \ie{}, it finds that no other
option can be removed. The procedure uses negative traffic to guide
the search.

@@

>>>>

The seed rule produced in the first step satisfies the criterion to
only capture positive traffic. However, that rule is overconstrained.
It could include options that are irrelevant to capturing the attack
and could lead to false negatives---the \nids\ may be unable to
capture manifestations of the same attack whose messages do not
exhibit the data satisfying irrelevant options.

@@

\tname{} leverages public data sets~\cite{tcpreplay} of benign traffic
to guide the search for more general rules, hence addressing the
overffiting issue. To that end, \tname{} \emph{minimizes} the rules
produced in the previous step, preserving the invariant of \emph{only}
capturing the positive malicious traffic. We say that a rule is
minimal if discarding any option results in the capture of negative
(\ie{}, benign) traffic.  The minimization procedure we propose in
this step builds on the observation that all options from the rule
produced in the previous step are satisifed by the positive
traffic. Consequently, any subset of these options also captures the
positive traffic. The minimization procedure that we describe in the
following iteratively discards options from visited rules---derived
from the seed rule---using the negative traffic to guide the search
for minimal rules.

@@

\Mar{--------------------------------------- estou aqui}
